% RESUME
%   Penn Bauman
%   pennbauman@protonmail.com
%   2020-12-06

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[top=0.8in,bottom=0.8in,left=1in,right=1in,centering,letterpaper]{geometry}
\usepackage{latexsym}
\usepackage[osf]{mathpazo}
\usepackage{titlesec}
\usepackage{hyperref}
\author{Penn Bauman}

%\definecolor{maia}{HTML}{2EB398}
\titleformat{\section}[display]{\Large\bfseries}{\thesection}{0.5em}{}[]
\titlespacing{\section}{0pt}{12pt}{2pt}
\hypersetup{colorlinks=false}
\thispagestyle{empty}

% Disable line wrapping
\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

% Set font DejaVu Sans Mono
\usepackage{DejaVuSansMono}
\renewcommand*\familydefault{\ttdefault}
\usepackage[T1]{fontenc}



\begin{document}
\normalfont
\begin{center}
	{\huge \textbf{Penn Bauman}}
\end{center}

\vspace*{1mm}

\noindent 4905 15th St N, Arlington, VA
\hspace*{\fill}
703-963-2729

\vspace*{1mm}

\noindent \href{https://pennbauman.com}{pennbauman.com}
\hspace*{\fill}
\href{mailto:pennbauman@protonmail.com}{pennbauman@protonmail.com}




\section*{Professional Experience}

\noindent \textbf{Green America} (\href{https://greenamerica.org}{greenamerica.org})
\hspace*{\fill} June - August 2018, 2019

\textit{Digital Products Associate, Independent Contractor}

\noindent Worked with the Drupal content management system on website layout and design, database searching, and Google Maps API.


\vspace*{4mm}


\noindent \textbf{Undergraduate Teaching Assistant}
\hspace*{\fill} September 2020 - Present

\textit{CS 2150: Program and Data Representation}

\noindent Responsible for holding one-on-one labs and office hours to assist students with development of programming skills and understanding. 




\section*{Education}

\noindent \textbf{University of Virginia} (GPA: 3.7)
\hspace*{\fill} 2018 - 2022 (Expected)

\textit{Bachelor of Science in Computer Science with a Minor in Physics}

\noindent Related Course Work:
Data Structures, Theory of Computation, Algorithms,
Software Engineering, Computer Architecture,
Linear Algebra, Differential Equations, Probability,
Modern Physics, Classical Mechanics



\section*{Skills}

\noindent\textbf{Public Speaking:} Ability to engagingly articulate ideas both in person and through digital mediums.

\noindent\textbf{Languages \& Technologies:}
	C/C++,
	Java,
	Rust,
	Python, Django, Flask,
	PHP, SQL, HTML,
	CSS, Sass, Bootstrap,
	Javascript, ReactJS,
	Drupal,
	Linux, Bash,
	LaTeX



\section*{Projects \href{https://github.com/pennbauman}{\textmd{\normalsize (github.com/pennbauman)}}}

\noindent\textbf{IBCM Executor:} \textit{C}
\hspace*{\fill} 2020

\noindent A custom executor and debugger for the Itty Bitty Computing Machine, a language created by UVA professors to teach the basics of machine code.


\vspace*{1mm}


\noindent\textbf{Civic Connect Web App:} \textit{Python, Django, HTML, Bootstrap}
\hspace*{\fill} 2020

\noindent An site, build using the Django Python web framework, that allows users to create and view shareable email messages for their elected representatives.


\vspace*{1mm}


\noindent\textbf{Personal Website:} \textit{PHP, SQL, HTML, CSS, Sass}
\hspace*{\fill} 2018 - Present

\noindent Used to develop web developmets skills from design to databse management. Also includes a custom spreadsheet system built to track my finances.


\vspace*{1mm}


\noindent\textbf{Assassins Web App:} \textit{PHP, SQL, HTML, CSS}
\hspace*{\fill} 2018

\noindent A from scratch web application used to organize a school wide game of assassins with user accounts and database management.


\end{document}
